05-applying_lime

### 2019-02-21 journals/05-applying_lime.Rmd
moved old lime results to new folder for time being

```{r}
# Load libraries
library(tidyverse)

@@

```{r}
# Read in the Hamby 224 test data
hamby224_test <- read.csv("../data/hamby224_test.csv")

# Read in the test_explain data
hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
```

@@

```{r}
# Obtain features used when fitting the rtrees random forest
rf_features <- rownames(bulletr::rtrees$importance)
```

>>>>

```{r}
# Load libraries
library(bulletr)
library(lime)
library(furrr)
library(future)
library(randomForest)
library(tidyverse)

# Load rtrees into session
data("rtrees")

@@

```{r}
# Load in the training data (Hamby Data 173 and 252)
hamby173and252_train <- read.csv("../data/hamby173and252_train.csv")

# Load in the testing data (Hamby Data 224 Sets 1 and 11)
hamby224_test <- read.csv("../data/hamby224_test.csv")
```

@@

```{r}
# Obtain features used when fitting the rtrees random forest
rf_features <- rownames(rtrees$importance)
```
